Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-03-30 paper.tex
Cite our implementation

\section{Results}
\label{sec:results}
In this section we will provide few examples of sets for which the developed
precise algorithm is applicable and compare the surface-surface function
calculated with the fast algorithm (\cref{sec:algo}) with results of the new
algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
paper.

@@

\subsection{Gaussian mixture}
\label{sec:gauss}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth, frame]{images/blob.png}
  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
    which consists of four Gaussian functions. White area is where
    $f(x,y) \le 3$.}
  \label{fig:blob}
\end{figure}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\cref{fig:blob}. We can use the algorithm developed in \cref{sec:fss-2d} to
compute precise values of $F_{ss}$ for this blob and compare them with values
obtained by using the fast algorithm in section \cref{sec:algo}. The result of
this comparison is on \cref{fig:fss-blob}.
\begin{figure*}[!hpt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
    \label{fig:fss-blob-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
    \label{fig:fss-blob-5x5}}
  \caption[]{Plot of the surface-surface function for the blob on
    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-blob}
\end{figure*}

@@

\section{Conclusion}
% Is this a right label?
\label{sec:summary}
In this paper we develop an algorithm for precise calculation of surface-surface
correlation function for two-dimensional sets with smooth boundary and checked
our fast algorithm using these new cases. The fast algorithm was improved using
a wider filter $H'$.

@@

>>>>

\section{Results}
\label{sec:results}
In this section we will provide few examples of sets for which the developed
precise algorithm is applicable and compare the surface-surface function
calculated with the algorithm for digital images (\cref{sec:algo}) with results
of the new algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
paper.

@@

\subsection{Gaussian mixture}
\label{sec:gauss}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth, frame]{images/blob.png}
  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
    which consists of four Gaussian functions. White area is where
    $f(x,y) \le 3$.}
  \label{fig:blob}
\end{figure}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\cref{fig:blob}. We can use the algorithm developed in \cref{sec:fss-2d} to
compute precise values of $F_{ss}$ for this blob and compare them with values
obtained by using the algorithm in section \cref{sec:algo}. The result of this
comparison is on \cref{fig:fss-blob}.
\begin{figure*}[!hpt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
    \label{fig:fss-blob-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
    \label{fig:fss-blob-5x5}}
  \caption[]{Plot of the surface-surface function for the blob on
    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-blob}
\end{figure*}

@@

\section{Conclusion}
% Is this a right label?
\label{sec:summary}
In this paper we develop an algorithm for precise calculation of surface-surface
correlation function for two-dimensional sets with smooth boundary and checked
our algorithm for digital images using these new cases. The algorithm was
improved using a wider filter $H'$.

@@

An implementation of the precise algorithm for sets with smooth boundary is
available on GitHub\cite{diff-boundary-corrfn}.
